Positive Relationship between a Country's Employment Rate and Permanent Immigrant Inflows

### 2023-04-17 outputs/paper/paper.qmd
Update with population

```{r}
#| include: false
#| warning: false
#| message: false
#| 
#### Initialize quarto workspace by reading csv's ####
library(tidyverse)
library(here)

@@

@@

#| label: fig-1
#| fig-cap: A graph detailing that the overall increase in the permenant immigration inflow from 2008 to 2019 is from...
#|  mean highest education level percentage of women over a 20 year period from 2000 to 2021 is from 13.0 to 13.7.
#| echo: false
#| warning: false

@@

>>>>

```{r}
#| include: false
#| warning: false
#| message: false

#### Initialize quarto workspace by reading csv's ####
library(tidyverse)
library(here)

@@

## Permanent Immigrants Inflows from 2009 to 2019

@@

#| label: fig-1
#| fig-cap: A graph detailing that the overall increase in Canada's permenant immigration inflow from 2009 to 2019 which is from 249292 to 341173.
#| echo: false
#| warning: false

merged_data %>%
  group_by(Year) %>%
  summarize(Permanent_Inflows = sum(Permanent_Inflows, na.rm = TRUE)) %>%
  ggplot(aes(x = Year, y = Permanent_Inflows)) +
  geom_line(group = 1, color = "red") +
  scale_x_continuous(breaks = seq(2009, 2019, by = 1), labels = c("2009", "2010", "2011", "2012", "2013", "2014", "2015", "2016", "2017", "2018", "2019")) +
  theme_bw() +
  labs(
    title = "Permanent Immigrants Inflows in Canada from 2009 to 2019",
    x = "Year",
    y = "Permanent Immigrants Inflows" 
  )

\
## Employment Rate from 2009 to 2019

#| label: fig-1
#| fig-cap: A graph detailing that the overall increase in Canada's permenant immigration inflow from 2009 to 2019 which is from 249292 to 341173.
#| echo: false
#| warning: false

merged_data %>%
  group_by(Year) %>%
  summarize(Employment_Rate = sum(Employment_Rate, na.rm = TRUE)) %>%
  ggplot(aes(x = Year, y = Employment_Rate)) +
  geom_line(group = 1, color = "blue") +
  scale_x_continuous(breaks = seq(2009, 2019, by = 1), labels = c("2009", "2010", "2011", "2012", "2013", "2014", "2015", "2016", "2017", "2018", "2019")) +
  theme_bw() +
  labs(
    title = "Employment Rate in Canada from 2009 to 2019",
    x = "Year",
    y = "Employment Rate" 
  )

@@

$$
Pr(\theta | y) = \frac{Pr(y | \theta) Pr(\theta)}{Pr(y)}
$$ {#eq-bayes}

The goal of our modelling strategy is twofold. Firstly,...

Here we briefly describe the Bayesian analysis model used to investigate... Background details and diagnostics are included in [Appendix -@sec-model-details]

## Model set-up

We run the model in R [@citeR] using the `rstanarm` package of @rstanarm. We use the default priors from `rstanarm`.
